\documentclass[12pt]{article}
\usepackage[letterpaper,margin=1in]{geometry}
\usepackage{tabu}
\usepackage{fontawesome}
\usepackage{academicons}
\usepackage{multirow}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[compact]{titlesec}
\usepackage{tabularx}

\pagenumbering{gobble}

%%% Macros with contact information %%%
\newcommand{\address}{} %Currently set up to be 3 lines.
\newcommand{\email}{}
\newcommand{\phone}{}
\newcommand{\website}{}
\newcommand{\twitter}{}
\newcommand{\linkedin}{}
\newcommand{\github}{}
\newcommand{\twitch}{}
\newcommand{\user}{}
\newcommand{\steam}{}
% \newcommand{\orcid}{}

%%% Reduce section spacing
%%% Keep the contact information in a separate file %%%

\input{contactinfo}

%%% Content

\begin{document}
{\noindent\huge{\textbf{Adam James Orr\\}}}

\noindent
\begin{tabular}{l l l}
	%\setlength{\tabcolsep}{1pt}
	\multirow{3}{*}{\begin{tabular}{@{}l @{}l@{}}
		\multirow{3}{*}{\faicon{map-marker} } & \address{}
	\end{tabular}} & \faicon{envelope-o} \email{} & \faicon{phone} \phone{} \\
	& \faicon{link} \url{\website} & \faicon{twitter} \twitter{} \\
	& \faicon{linkedin} \url{\linkedin} & \faicon{github} \url{\github} \\
	\faicon{user} \user{} & \faicon{steam-square} \steam{} & \faicon{twitch} \url{\twitch}
\end{tabular}

\section*{\faicon{bullseye} Objective}

Build, test, and interpret models to make inferences and forecasts that inform decision-making and help teams achieve their goals.

\section*{\faicon{graduation-cap} Education}

\begin{tabular}{p{.33\linewidth} p{.33\linewidth} p{.33\linewidth}}
    PhD. Molecular and Cellular Biology & B.S. Mathematics & B.S. Molecular Biology and Biotechnology \\
    August 2015 - Present & August 2011 - May 2015 & August 2011 - May 2015 \\
    Arizona State University & Arizona State University & Arizona State University
\end{tabular}

\section*{\faicon{gears} Technical Skills}

\textbf{\faicon{heart}\faicon{heart}\faicon{heart} Used Daily}
Computing with UNIX; Programming with R and Python; Data manipulation with dplyr, purrr, numpy, scipy; Plotting with ggplot2, matplotlib, seaborn; Writing reports with \LaTeX, Rmarkdown, Jupyter Notebook \\
\textbf{\faicon{heart-o}\faicon{heart}\faicon{heart} Intermediate Knowledge}
Programming with Perl, C++, Java, Android, Matlab; Data manipulation with pandas; Modeling with scikit-learn, Stan; Version Control with git\\
\textbf{\faicon{heart-o}\faicon{heart-o}\faicon{heart} Basic Familiarity}
MySQL, tensorflow

\section*{\faicon{history} Experience}

\noindent \textbf{Research Assistant} \hfill{} August 2014 - Present\\
Cartwright Lab - Arizona State University \hfill{} \faicon{link} \url{cartwrig.ht/lab/}
\begin{itemize}[nosep, leftmargin=*]
\item Analyzed the calibration of error probabilities in DNA sequencing data. Developed and tested a hierarchical model to correct poorly calibrated sequences.
\item Used Hidden Markov Models to classify substrings of DNA sequences.
\item Development and application of a maximum likelihood approach for detecting mutations and estimating model parameters in DNA sequencing data. 
\end{itemize}

\noindent \textbf{Certified Workshop Instructor} \hfill{} May 2016 - Present\\
The Carpentries \hfill{} \faicon{link} \url{carpentries.org}
\begin{itemize}[nosep, leftmargin=*]
\item \textit{The Carpentries} is a non-profit organization dedicated to teaching computing and data science skills to researchers.
\item Taught 2-day Software Carpentry workshop (Bash, Git, and R) at Arizona State University %\faicon{link} \url{https://www.adamjorr.com/2016-05-23-BiodesignASU/}
and 2-day Data Carpentry workshop (Bash, Data Wrangling for Genomics, Cloud Computing for Genomics) at Lawrence Berkeley National Laboratory. % \faicon{link} \url{https://code.nimahejazi.org/2018-05-03-LBNL/}
\item Taught the 2-week Carpentries-style ANGUS Bioinformatics workshop at UC Davis (Helper 2017, Lead Instructor 2018).
\end{itemize}

%\section*{\faicon{gamepad} Extracurricular Activities}



\end{document}



